---
title: "tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(linreg)
library(bench)
```

## Overview
The linreg function fits a linear regression model on a numeric vector (y) and a numeric vector or list of numeric vectors (x).
```{r}
mpg = mtcars[,1]
cyl = mtcars[,2]
disp = mtcars[,3]

# x: one vector of covariates
linreg(mpg, list(cyl = cyl))

# x: a list of multiple vectors
linreg(mpg, list(cyl = cyl, disp = disp))
```
If a dataset is specified, and the function looks for parameters y and x first in the column names of the dataset (in which case, they must be written in quotation marks), then in the environment. 
```{r}
# y and x are columns from the dataset
linreg("hp", list(drat = "drat"), mtcars)

# vectors from outside the dataset can be included
linreg(mpg, list(cyl = cyl, drat = "drat"), mtcars)
```

## Performance
The output's correctness can be verified by the lm function. 
```{r}
test1 = as.matrix(linreg("hp", list(cyl = "cyl"), mtcars))
test2 = summary(lm(hp ~ cyl, data = mtcars))$coefficients

all.equal(as.vector(test1), as.vector(test2))
```
The linreg function is approximately 7 times more efficient than lm at parameter estimation and inference. The trade-off is that linreg does not provide additional model information, such as F-statistic. 
```{r, fig.dim = c(6, 3)}
set.seed(625)
benchtesty = rnorm(1e5)
benchtestx = rnorm(1e5)

time = bench::mark(as.vector(as.matrix(linreg(benchtesty, list(benchtestx = benchtestx)))),
                   as.vector(summary(lm(benchtesty ~ benchtestx))$coefficients))

time[,1] = c("linreg","lm")
print(time)
```

